Computer Science House Constitution

### 2023-10-29 constitution.tex
Merge 2.C.3 and 2.C.4 (#97)
Allow Maintainers to be Alumni in bad standing (#98)

\asubsection{Maintainer Qualifications}
Maintainers must be Active or Alumni in good standing.

@@

\asubsection{Maintainer Resignations}
Maintainers may resign at any time by notifying the current Executive Board and Maintainer group.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.

>>>>

\asubsection{Maintainer Qualifications}
Maintainers must be Active or Alumni Members.

@@

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
